\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-18 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
changement texte

\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}}-1 \right) + \epsilon_{ik} \label{eq:equation0}
\end{equation}

\textbf{STOP HERE XXXX }

Since Equation (\ref{eq:equation0}) is non-linear, it cannot be estimated using standard linear estimators. All estimates are thus performed using non-linear least squares.\footnote{The basis of the method is to approximate the model by a linear one and to refine the parameters by successive iterations. The intuitive criterion for convergence is that the sum of squares of residuals does not increase from one iteration to the next.
See \cite{Woolridge-Book-2001} for more details.} Yet, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time.
Confronted with this trade-off, we estimate international transport costs at the 3-digit level as our benchmark classification, even though data series are available at a more disaggregated product level ($k=5$ in our benchmark estimates). This amounts to making the additional assumption, that all 5-digit products $k$ in a 3-digit sector $s$ share the same structure of costs.\footnote{One way to gauge the relevance of this assumption is to provide a decomposition variance exercise on the observed cif-fas price.
As reported in the Online Appendix, Section D.1, the share of the observed variance that is accounted for by the between-sectors ($s$) variance is roughly similar to the between-product ($k$) variance.}$^{,}$\footnote{One may object that we could preserve the estimation at the 5-digit level by running an OLS estimation on the equation taken in level, i.e.
on the basis of Equation (\ref{eq:base_estimee}), specifying the error term additively.
This would not solve the problem though, for three main complementary reasons.
First, at the 5-digit level the number of fixed effects to include in the estimation would be more than 430,000 (with 216 countries and 2,029 products), making the estimation computationally extremely burdensome, even in OLS.
Imposing Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) to reduce the number of fixed effects would drive us back to the non-linearity issue for fixed effects.
Second, making the error term (specified as following a normal law centered on 0) enter Equation (\ref{eq:base_estimee}) additively implies negative values for some of the estimated residuals $\widehat{\epsilon}_{ik}$, which is inconsistent with the constraint that $\frac{p_{ik}}{\widetilde{p}_{ik}}>1$.
Third, estimating the equation in level does not eliminate the fact that it is non-linear by nature, as long as there are additive costs to estimate (see Equation (\ref{eq:base_estimee}) for $t_{ik} \neq 0$).}

This drives us to estimate a modified version of Equation (\ref{eq:equation0}), specified as:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times \tau_{s(k)} -1+\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}} \right) + \epsilon_{ik} \label{eq:model_IetA}
\end{equation}
where $\tau_{i}$, $\tau_{s(k)}$, $t_{i}$ and $t_{s(k)}$ are the parameters to be estimated, i.e., fixed effects specific to each origin country $i$ and sector $s$ (at the 3-digit classification level), and $\epsilon_{ik}$ the residual centered on 0.\footnote{Note that, strictly speaking, the exact equation that we estimate is the following:
$$\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\sum_i \alpha_i^\tau \mathbbm{1}_i \times \sum_{s(k)}\alpha_{s(k)}^\tau \mathbbm{1}_{s(k)}-1 + \frac{\sum_i\alpha_i^t\mathbbm{1}_i + \sum_{s(k)}\alpha^t_{s(k)}\mathbbm{1}_{s(k)}}{\widetilde{p}_{ik}}\right)+\epsilon_{ik} $$
After proceeding to the estimation, we uncover the estimated values of the transport costs components $\tau_{i}$, $\tau_{s(k)}$, $t_{i}$, $t_{s(k)}$ from the obtained coefficients $\alpha^{x}_{z}$ for $x=\tau,t$ and $z=i,s(k)$ (by year and transport mode).
For reading convenience, we adopt a lighter expression of this equation by resorting to the notations of $\tau_i,\tau_{s(k)}$ and $t_i$, $t_{s(k)}$ as a short-cut.}  To eliminate the potential influence of outliers, we exclude 5\% of the upper and lower tails of the distribution in the regression variables.
%JH: TO KEEP IN MIND: one day, we could be asked to winsorize tails, instead of cutting them...
These cut-offs are aimed at eliminating reporting or coding errors.
We estimate Equation (\ref{eq:model_IetA}) for each year over the period 1974-2019, for each of the transportation modes reported (air or vessel), on a sectoral-origin country basis ($i,s$).
Depending on the year considered, this leaves us with around 800 fixed effects to estimate by transport mode at the 3-digit level.
  \medskip

As mentioned in the Introduction, one contribution of the paper is to provide a careful estimation of international transport costs, which decomposes into both an additive and an ad-valorem component. We do so by adopting the following strategy. For each year and transport mode, we estimate two models. In Model (A), additive costs are excluded, transport costs being modeled as ad-valorem costs only. In this case, the estimated equation simplifies as:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times\tau_{s(k)}-1 \right) + \epsilon^{ice}_{ik} \label{eq:model_nlI}
\end{equation}

Under Model (B), transport costs are decomposed in the two additive and ad-valorem dimensions (Equation (\ref{eq:model_IetA})).
From this, we compare the fitting properties and the explanatory power of both models to evaluate the importance of modeling the additive component.\footnote{One may object that a comprehensive study of the structure of transport costs should also include the third model with only additive costs. This has driven us to estimate this third model (c) as well, in which case the estimated equation is written according to: $\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}}\right) + \epsilon^{add}_{ik}$.
The main result that emerges is that this model (c) is dominated (in terms of quality of fit properties) by the model (A) with multiplicative costs only, which is itself dominated by the complete model (B), anticipating further results. More details of these results are given in the Online Appendix.}

%One may be concerned that the specification of Equations (\ref{eq:model_IetA}) or (\ref{eq:model_nlI}) might be subject to an endogeneity bias, as the price set by the exporter may vary depending on the transport cost burden.
%Studies on the pricing-to-market behavior of firms (see \citealp{Krugman-87}) show that we cannot exclude that the export price set by the firm ($\widetilde{p}_{ik}$) is partly endogenous to the size of transport costs (for instance, the exporting firm absorbing (part of) the transport costs by reducing the fas price).
%This is not an issue here, as we are not interested in causal inference.
%Rather, our aim is to provide an accounting breakdown of transport costs between the additive and the multiplicative components.

%\textbf{pas encore completement clair. Veut-on dire que ce qui est pbtique, c'est que TC reagisse a ptilde? Je crois que ce qu'on veut dire, c'est que le fait que ptilde change en fonction des TC ne change pas les TC, le cif price s'ajuste proportionnellement? Si c'est ca, c'est vrai seulement si les couts sont advalorem...Pour dire que les firmes peuvent difficilement influencer le prix du transport au niveau 3d, on pourrait donner des stats des la dessus? Par produit 3d/pays, par secteur 3d tous pays, etc...?}\smallskip

After estimating Equation (\ref{eq:model_IetA}), we can rebuild a measure of each component, $\widehat{\tau}^{adv}_{is(k)} = \widehat{\tau_{i}} \times \widehat{\tau}_{s(k)}$ for the ad-valorem cost and $\widehat{t}_{is(k)} = \widehat{t}_{i} + \widehat{t}_{s(k)}$ for the additive cost, that are country-sector specific, by year and transport mode.
When assuming ad-valorem costs only (Equation (\ref{eq:model_nlI})), we proceed similarly to get $\widehat{\tau}^{ice}_{is(k)} = \widehat{\tau}_{i} \times \widehat{\tau}_{s(k)}$.
In this case, notice that the equation could be estimated relying on a linear form.
To preserve comparability of the results, we keep the same non-linear estimation method in both cases.
Similarly, as \cite{Irrazabal_2015}, we take the average over the sector-country dimension, using the values of each trade flow ($is$-specific) over total yearly trade as a weighting scheme.
We thus recover a ``synthetic estimate'' of each type of transport cost: $\widehat{\tau}^{ice}$ for Model (A), $\widehat{\tau}^{adv}$ and $\widehat{t}$ for Model (B), for each year and transportation mode.
These results are reported in Section \ref{sec:results_decomposition}.

@@

%Our ambition to re-assess the underlying sources of the trend patterns of international transport costs requires a careful modeling of both the additive and the multiplicative components.
\paragraph{Quantification} The first step of the analysis consists of providing a quantification of the magnitude of transport costs over time (by transport mode), distinguishing whether the additive component $t_{ik}$ is excluded or included in the estimated equation (Equation (\ref{eq:model_IetA}) or (\ref{eq:model_nlI})).
This allows us to provide estimates for the size of both the ad-valorem and the additive components of transport costs, and assess whether additive costs represent a sizable component of the latter.
These results constitute our first original contribution to the literature.
\smallskip

@@

Table \ref{tab:summary_results} reports a summary of our results.
It displays the weighted mean and median values of each type of transport costs (either ad-valorem estimated alone or estimated along with additive costs), as well as the associated standard deviation, averaged over the period 1974-2019, for estimation driven both at the 3- and 4-digit sectorial level for different specifications and data.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport modes, at the 3- and 4-digit classification level. Results for all years (available at the 3-digit level) are reported in the Online Appendix, available on the authors' webpages.}
The top panel reports the same set of descriptive statistics, but for the actual cif/fas ratio in our data. In the medium panel, we report the results for a specification based on ad-valorem costs estimated alone (Model (A), based on Equation (\ref{eq:model_nlI})). The bottom panel presents our estimates for a specification involving both ad-valorem and multiplicative components (Model (B), based on Equation (\ref{eq:model_IetA})).

@@

Before jumping to the interpretation, Table \ref{tab:summary_results} calls for two comments of statistical order. First, the estimated mean values are systematically higher than medians. This result is not surprising though, given that our key variable is by nature bounded to 0; therefore, outliers can only be positive, pushing the mean upward compared to the median. Second, the estimated total costs are not exactly equal to the observed ones, in particular for Model (A). This might be accounted for by recalling that all our estimates are based on log-linearization. Therefore, what matters on the statistical ground is that the mean of our predicted values (based on logarithms) must be equal to the mean of the log-linearized data ($\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)$), which does not necessarily imply equality between values.
Descriptive statistics showing that both observed and predicted values do match in logarithms are available upon request to the authors.

@@

\paragraph{Interpretation} Coming now to interpretation, two main results emerge from Table \ref{tab:summary_results}.
First, it provides estimation results about the size of the overall transport costs.
Table \ref{tab:summary_results} shows that transport costs amount to around a 5.5-6\% markup in ocean shipping, and 4\% markup in air shipping on average over 1974-2019.\footnote{Expressed as a markup over production costs, transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}}$.
Under Model (A) (ad-valorem costs only), this gives a markup of 5.5\% in vessel, and 4.8\% in air shipping (considering the mean value over the period).
Under Model (B), total transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}} = (\tau-1) + \frac{t}{\widetilde{p}}$.
With $\tau= 1.030$ and $\frac{t}{\widetilde{p}}= 0.028$ in vessel (as reported in Table \ref{tab:summary_results}), we get a value equal to 5.8\%.
A similar calculus gives 4.1\% in air transport.} If this seems modest in comparison with the 11\% of markup obtained by \cite{anderson_wincoop_jel} over a set of industrialized countries, it stands in line with the results obtained by \cite{hummels2007} for the US economy.\footnote{Beyond country coverage and time period, another plausible explanation for the difference with \cite{anderson_wincoop_jel}, lays in the difference of empirical methodology.
\cites{anderson_wincoop_jel} estimates are based on standard gravity equations, while ours come from a non-linear estimation of a ``structural'' decomposition of the difference between export and import prices.}

Second, and most importantly, Table \ref{tab:summary_results} provides new quantitative evidence about the size of the additive component of transportation costs.
On average over the whole period, for sectors defined at the 3-digit level, additive costs amount to around 10 cents (0.1 USD) per kilogram exported in maritime transport, and 1.13 USD per kilogram exported in air transport, indicating that freight rates are much higher in the latter case.
Expressed in terms of the export price, the additive costs amount to 2.8\% and 1.7\% for ocean shipping and air transport respectively.
This is slightly lower than the estimates for the ad-valorem component, which is estimated at 3\% and 2.4\% for vessel and air shipping respectively (on average over the period).
Put differently, the additive component amounts to 44\% of total transport costs in vessel, and 30\% in Air, as displayed in the last rows of Table \ref{tab:summary_results}: The per-kg cost dimension is quantitatively sizable.
\medskip

We also provide diagnostic tests about the goodness-of-fit measures, which confirm the empirical relevance of adding the additive component in the estimation. Appendix \ref{app:diagnostic_test} reports quality-of-fit diagnostic tests that confirm the importance of the additive cost component.
The goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the removed degree of freedom. For both transport modes, the omission of the additive term seriously biases the ad-valorem term upward, by roughly a factor 2.\smallskip

Our estimation results on the size of additive transport costs can be compared to \cite{Irrazabal_2015}, the most recent evidence on this question.
Based on Norwegian trade data for 2004, \cite{Irrazabal_2015} estimate that additive costs (in Norwegian crowns) amount to 6\% of export price multiplied by the ad-valorem cost (expressed in Norwegian crowns), i.e.
$\frac{t}{\tau\widetilde{p}}=6\%$ expressed in our terminology (with $\tau>1$, and retaining their estimated weighted mean value, which is the one directly comparable to our own results).
One important difference with respect to their work is that we can provide separate estimates for each cost component (additive and ad-valorem).
From this, we can rebuild the ratio in similar terms to them, allowing us to gain in generality in this respect.
Making use of our estimates for 2004 (see Tables \ref{tab:result_air_3d_detail} and \ref{tab:result_ves_3d_detail} in Appendix \ref{app:more_results}), we thus obtain a ratio $\frac{t}{\tau\widetilde{p}}=2.8\%$ in ocean shipping and 1.5\% in air transport.
This may seem surprisingly low, in contrast to the 6\% obtained by \cite{Irrazabal_2015}.
This can be accounted for by recalling the difference in the type of dataset - hence, of costs, embraced in each case.
While the database of \cite{Irrazabal_2015} allows studying trade costs in general, our database covers a subset made of the monetary international transport costs, as we start from the gap between the import and the export prices (on top of differences due to the country coverage of the two databases).
In this respect, our two papers can be used in a complementary fashion to infer the proportion of additive trade costs that are due to international shipment.
\cites{Irrazabal_2015} results on the year 2004 imply that, for an export price multiplied by the ad-valorem cost of 100 USD, 6 USD are paid in additive trade costs.
For the same export price multiplied by the ad-valorem cost of 100 USD, our results for 2004 yield the value of 2.8 (1.5) USD paid in additive transport costs for maritime (air) transport.\footnote{Also notice that, in both papers, starting from the estimated value of the ratio $\frac{t}{\tau \widetilde{p}}= x$, we can rebuild the proportion of additive costs in terms of the import price $\frac{t}{\tau \widetilde{p} + t} = \frac{x}{1+x}$.
Given our estimates for 2004 ($x = 0.028$ and $0.015$ in vessel and air transport respectively), we get a ratio $\frac{t}{\tau \widetilde{p} + t}$ equal to 2.7\% and 1.4\% in each transport mode respectively.} This comparison of results suggests that between 25\% (air) and 47\% (vessel) of additive trade costs are attributable to international transport.
On top of our results summarized in Table \ref{tab:summary_results}, this points to evidence that the additive component represents a quantitative sizable dimension of international transport costs.\smallskip

>>>>

\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}}-1 \right) + \epsilon_{ik}, ~\text{with } \tau_{i}\geq 1, \tau_{k}\geq 1, t_{i}\geq 0  ~\text{and }t_{k}\geq 0  \label{eq:equation0}
\end{equation}

\noindent where we ensure the positivity constraint on $\tau_x-1$, $t_x$ (with $x =i,k$) by taking logs.

Since Equation (\ref{eq:equation0}) is non-linear, it cannot be estimated using standard linear estimators. All estimates are thus performed using non-linear least squares.\footnote{The basis of the method is to approximate the model by a linear one and to refine the parameters by successive iterations. The intuitive criterion for convergence is that the sum of squares of residuals does not increase from one iteration to the next.
See \cite{Woolridge-Book-2001} for more details.} Yet, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time.
Confronted with this trade-off, we estimate 3-digit level sectoral fixed effects as our benchmark. This amounts to making the additional assumption, that all 5-digit products $k$ in a 3-digit sector $s$ share the same structure of costs.\footnote{One way to gauge the relevance of this assumption is to provide a decomposition variance exercise on the observed cif-fas price.
As reported in the Online Appendix, Section D.1, the share of the observed variance that is accounted for by the between-sectors ($s$) variance is roughly similar to the between-product ($k$) variance.}$^{,}$\footnote{One may object that we could preserve the estimation at the 5-digit level by running an OLS estimation on the equation taken in level, i.e.
on the basis of Equation (\ref{eq:base_estimee}), specifying the error term additively.
This would not solve the problem though, for three complementary reasons.
First, at the 5-digit level the number of fixed effects to include in the estimation would be more than 430,000 (with 216 countries and 2,029 products), making the estimation computationally extremely burdensome, even in OLS.
Imposing Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) to reduce the number of fixed effects would drive us back to the non-linearity issue for fixed effects.
Second, making the error term (specified as following a normal law centered on 0) enter Equation (\ref{eq:base_estimee}) additively implies negative values for some of the estimated residuals $\widehat{\epsilon}_{ik}$, which is inconsistent with the constraint that $\frac{p_{ik}}{\widetilde{p}_{ik}}>1$. In a related manner, we could not impose positivity constraints on the coefficients. Third, estimating the equation in level does not eliminate the fact that it is non-linear by nature, as long as there are additive costs to estimate (see Equation (\ref{eq:base_estimee}) for $t_{ik} \neq 0$).}

This drives us to estimate a modified version of Equation (\ref{eq:equation0}), specified as:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times \tau_{s(k)} -1+\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}} \right) + \epsilon_{ik} \label{eq:model_IetA}
\end{equation}
where $\tau_{i}$, $\tau_{s(k)}$, $t_{i}$ and $t_{s(k)}$ are the parameters to be estimated, i.e., fixed effects specific to each origin country $i$ and sector $s$ (at the 3-digit classification level), and $\epsilon_{ik}$ the residual centered on 0.\footnote{Note that, strictly speaking, the exact equation that we estimate is the following:
$$\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\sum_i \alpha_i^\tau \mathbbm{1}_i \times \sum_{s(k)}\alpha_{s(k)}^\tau \mathbbm{1}_{s(k)}-1 + \frac{\sum_i\alpha_i^t\mathbbm{1}_i + \sum_{s(k)}\alpha^t_{s(k)}\mathbbm{1}_{s(k)}}{\widetilde{p}_{ik}}\right)+\epsilon_{ik} $$
After proceeding to the estimation, we uncover the estimated values of the transport costs components $\tau_{i}$, $\tau_{s(k)}$, $t_{i}$, $t_{s(k)}$ from the obtained coefficients $\alpha^{x}_{z}$ for $x=\tau,t$ and $z=i,s(k)$ (by year and transport mode).
For reading convenience, we adopt a lighter expression of this equation by resorting to the notations of $\tau_i,\tau_{s(k)}$ and $t_i$, $t_{s(k)}$ as a short-cut.}  To eliminate the potential influence of outliers, we exclude 5\% of the upper and lower tails of the distribution in the regression variables.
%JH: TO KEEP IN MIND: one day, we could be asked to winsorize tails, instead of cutting them...
These cut-offs are aimed at eliminating reporting or coding errors.
We estimate Equation (\ref{eq:model_IetA}) for each year over the period 1974-2019, for each of the transportation modes reported (air or vessel), on a sectoral-origin country basis ($i,s$). Depending on the year considered, this leaves us with around 400 fixed effects to estimate by transport mode at the 3-digit level.  \medskip

To drive home the importance of additive costs, we adopt the following strategy. For each year and transport mode, we estimate two models. In Model (A), additive costs are excluded, transport costs being modeled as ad-valorem costs only. In this case, the estimated equation simplifies as:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times\tau_{s(k)}-1 \right) + \epsilon^{ice}_{ik} \label{eq:model_nlI}
\end{equation}

In this case, notice that the equation could be estimated relying on a linear form. To preserve comparability of the results, we keep the same non-linear estimation method in both cases. Under Model (B), transport costs are decomposed in the two additive and ad-valorem dimensions (Equation (\ref{eq:model_IetA})).
From this, we compare the fitting properties and the explanatory power of both models to evaluate the importance of modeling the additive component.\footnote{One may object that a comprehensive study of the structure of transport costs should also include the third model with only additive costs. This has driven us to estimate this third model (C) as well, in which case the estimated equation is written according to: $\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}}\right) + \epsilon^{add}_{ik}$.
The main result that emerges is that this model (C) is dominated (in terms of quality of fit properties) by the model (A) with multiplicative costs only, which is itself dominated by the complete model (B). More details of these results are given in the Online Appendix, Section A.}

After estimating Equation (\ref{eq:model_IetA}), we can rebuild a measure of each component, $\widehat{\tau}^{adv}_{is(k)} = \widehat{\tau_{i}} \times \widehat{\tau}_{s(k)}$ for the ad-valorem cost and $\widehat{t}_{is(k)} = \widehat{t}_{i} + \widehat{t}_{s(k)}$ for the additive cost, that are country-sector specific, by year and transport mode.
When assuming ad-valorem costs only (Equation (\ref{eq:model_nlI})), we proceed similarly to get $\widehat{\tau}^{ice}_{is(k)} = \widehat{\tau}_{i} \times \widehat{\tau}_{s(k)}$.
As \cite{Irrazabal_2015}, we take the average over the country-sector dimension, using the values of each trade flow ($is$-specific) over total yearly trade as a weighting scheme.
We thus recover a ``synthetic estimate'' of each type of transport cost: $\widehat{\tau}^{ice}$ for Model (A), $\widehat{\tau}^{adv}$ and $\widehat{t}$ for Model (B), for each year and transportation mode. These results are reported in Section \ref{sec:results_decomposition}.

@@

%Our ambition to re-assess the underlying sources of the trend patterns of international transport costs requires a careful modeling of both the additive and the multiplicative components.
\paragraph{Quantification} The first step of the analysis consists in providing a quantification of the magnitude of transport costs over time (by transport mode), distinguishing whether the additive component $t_{ik}$ is excluded or included in the estimated equation (Equation (\ref{eq:model_IetA}) or (\ref{eq:model_nlI})).
This allows us to provide estimates for the size of both the ad-valorem and the additive components of transport costs, and assess whether additive costs represent a sizable component of the latter.
These results constitute our first original contribution to the literature.
\smallskip

@@

Table \ref{tab:summary_results} reports a summary of our results.
It displays the weighted mean and median values of each type of transport costs (either ad-valorem estimated alone or estimated along with additive costs), as well as the associated standard deviation, averaged over the period 1974-2019, for estimation driven both at the 3- and 4-digit sectorial level for different specifications and data.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport modes, at the 3- and 4-digit classification level. Results for all years (available at the 3-digit level) are reported in the Online Appendix.}
The top panel reports the same set of descriptive statistics, but for the actual cif/fas ratio in our data. In the medium panel, we report the results for a specification based on ad-valorem costs estimated alone (Model (A), based on Equation (\ref{eq:model_nlI})). The bottom panel presents our estimates for our baseline specification (Model (B), based on Equation (\ref{eq:model_IetA})).

@@

Before jumping to the interpretation, Table \ref{tab:summary_results} calls for two comments. First, the estimated mean values are systematically higher than medians. This result is not surprising though, given that our key variable is positive by nature; therefore, outliers can only raise the mean upward compared to the median. Second, the estimated total costs are not exactly equal to the observed ones, in particular for Model (A). This might be accounted for by recalling that all our estimates are based on log-linearization. Therefore, what matters on the statistical ground is that the mean of our predicted values (based on logarithms) must be equal to the mean of the log-linearized data ($\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)$), which does not necessarily imply equality between values. Descriptive statistics showing that both observed and predicted values do match in logarithms are available upon request to the authors.

@@

\paragraph{Interpretation} We now come to Table \ref{tab:summary_results}. First, the estimated size of overall transport costs amount to around a 5.5-5.8\% markup in ocean shipping, and 4.1-4.8\% markup in air shipping on average over the period.
%\footnote{Expressed as a markup over production costs, transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}}$. Under Model (A) (ad-valorem costs only), this gives a markup of 5.5\% in vessel, and 4.8\% in air shipping (considering the mean value over the period). Under Model (B), total transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}} = (\tau-1) + \frac{t}{\widetilde{p}}$. With $\tau= 1.030$ and $\frac{t}{\widetilde{p}}= 0.028$ in vessel (as reported in Table \ref{tab:summary_results}), we get a value equal to 5.8\%.
%A similar calculus gives 4.1\% in air transport.} 
If this seems modest in comparison with the 11\% of markup obtained by \cite{anderson_wincoop_jel} over a set of industrialized countries, it stands in line with the results obtained by \cite{hummels2007} for the US economy.\footnote{Beyond country coverage and time period, another plausible explanation for the difference with \cite{anderson_wincoop_jel}, lays in the difference of empirical methodology.
\cites{anderson_wincoop_jel} estimates are based on standard gravity equations, while ours come from a non-linear estimation of a ``structural'' decomposition of the difference between export and import prices.}

Second, and most importantly, Table \ref{tab:summary_results} provides new quantitative evidence about the size of the additive component of transportation costs.
On average over the whole period, for sectors defined at the 3-digit level, additive costs amount to around 10 cents (0.1 USD) per kilogram exported in maritime transport, and 1.13 USD per kilogram exported in air transport, indicating that freight rates are much higher in the latter case.
Expressed in terms of the export price, the additive costs amount to 2.8\% and 1.7\% for ocean shipping and air transport respectively.
This is slightly lower than the estimates for the ad-valorem component, which is estimated at 3\% and 2.4\% for vessel and air shipping respectively (on average over the period).
Put differently, the additive component amounts to 44\% of total transport costs in vessel, and 30\% in Air, as displayed in the last rows of Table \ref{tab:summary_results}: The per-kg cost dimension is quantitatively sizable.

We also provide diagnostic tests about the goodness-of-fit measures, which confirm the relevance of adding the additive component in the estimation. As reported in Appendix \ref{app:diagnostic_test}, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the fewer degrees of freedom.\smallskip

Our estimation results on the size of additive transport costs can be compared to \cite{Irrazabal_2015}, the most recent evidence on this question.
Based on Norwegian trade data for 2004, \cite{Irrazabal_2015} estimate that additive costs amount to 6\% of export price multiplied by the ad-valorem cost, i.e.
$\frac{t}{\tau\widetilde{p}}=6\%$ expressed in our terminology (with $\tau>1$, and retaining their estimated weighted mean value, which is the one directly comparable to our own results).
One important difference with respect to their work is that we can provide separate estimates for each cost component (additive and ad-valorem).
This allows building the ratio in similar terms to them, allowing us to gain in generality in this respect.
Making use of our estimates for 2004 (see Tables \ref{tab:result_air_3d_detail} and \ref{tab:result_ves_3d_detail} in Appendix \ref{app:more_results}), we thus obtain a ratio $\frac{t}{\tau\widetilde{p}}=2.8\%$ in ocean shipping and 1.5\% in air transport.
This may seem surprisingly low, in contrast to the 6\% obtained by \cite{Irrazabal_2015}.
This can be accounted for by recalling the difference in the type of dataset - hence, of costs, embraced in each case.
While the database of \cite{Irrazabal_2015} allows studying trade costs in general, our database covers a subset made of the monetary international transport costs, as we start from the gap between the import and the export prices (on top of differences due to the country coverage of the two databases).
In this respect, our two papers can be used in a complementary fashion to infer the proportion of additive trade costs that are due to international shipment.
\cites{Irrazabal_2015} results on the year 2004 imply that, for an export price multiplied by the ad-valorem cost of 100 USD, 6 USD are paid in additive trade costs.
For the same export price multiplied by the ad-valorem cost of 100 USD, our results for 2004 yield the value of 2.8 (1.5) USD paid in additive transport costs for maritime (air) transport.\footnote{Also notice that, in both papers, starting from the estimated value of the ratio $\frac{t}{\tau \widetilde{p}}= x$, we can rebuild the proportion of additive costs in terms of the import price $\frac{t}{\tau \widetilde{p} + t} = \frac{x}{1+x}$.
Given our estimates for 2004 ($x = 0.028$ and $0.015$ in vessel and air transport respectively), we get a ratio $\frac{t}{\tau \widetilde{p} + t}$ equal to 2.7\% and 1.4\% in each transport mode respectively.} This comparison of results suggests that between 25\% (air) and 47\% (vessel) of additive trade costs are attributable to international transport.
